Dismal Code: Studying the Evolution of Security Bugs

### 2013-04-03 docs/evol.tex
minor changes

\begin{keywords}
Software Bugs, Static Analysis, Software Evolution, Software
Security, Maven, FindBugs.
\end{keywords}

@@

Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories) are the most popular in the repository. This could be an indication
that programmers write code that implements the required functionality without considering
its many security aspects.
% An interesting observation is that 4,908 projects did not
% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
% This goes along with the relationship between the size of an artifact and it's
% bugs that is presented in the upcoming section.

@@

\section{Discussion}
\label{sec:dis}

>>>>

\begin{keywords}
Security Bugs, Static Analysis, Software Evolution, Software
Security, Maven, FindBugs.
\end{keywords}

@@

Figure~\ref{fig:bug-per} shows how software bugs are distributed among the
repository. Together with the {\it Bad Practice} bugs and the {\it Style} bugs,
security bugs (the sum of the {\it Security} and {\it Malicious Code}
categories) are the most popular in the repository ($\geq 22\%$).
This could be an indication that programmers write code that implements the
required functionality without considering its many security aspects.
% An interesting observation is that 4,908 projects did not
% have any bugs at all. These cases involved small artifacts with a minimum number of classes.
% This goes along with the relationship between the size of an artifact and it's
% bugs that is presented in the upcoming section.

@@

\section{Discussion}
\label{sec:dis}
% also mention:
% - the fact that we don't have the same number of versions in every project.
% - tell about the graph and Linus.
